\chapter{Objectives}
\label{ch:objectives}

The primary aim of this thesis is to develop an open-source, modular, and customizable drone capable of operating in remote areas. This drone will possess autonomous flight capabilities and the ability to communicate with a ground station. Furthermore, it will allow for remote control and can be programmed to perform specific tasks, making it suitable for various applications, including reconnaissance, surveillance, agriculture, and humanitarian aid.

In addition, a software platform will be developed to enable the programming of the drone for reconnaissance tasks. This software will be designed to support multiple drones, facilitating the creation of a coordinated swarm for reconnaissance operations.

The drone's design will emphasize ease of assembly, disassembly, repair, and maintenance. It will be cost-effective and user-friendly, allowing for straightforward customization and modification.

To achieve these objectives, the following specific aims will be pursued:

\begin{itemize}
  \item The design must be modular and customizable, enabling easy modifications to adapt the drone for different applications.

  \item The components utilized in the drone should be off-the-shelf and readily available, facilitating straightforward assembly and repairs.

  \item The drone must be capable of autonomous flight to enable operations in remote areas where manual control is challenging.

  \item The design will incorporate the latest advancements in drone technology, ensuring competitiveness with other market offerings.

  \item The drone must be capable of communicating with a ground station to facilitate remote control.

  \item The system should be programmable to perform specific tasks, such as reconnaissance of designated areas and monitoring of particular parameters.

  \item The software platform must support multiple drones, allowing for the deployment of a coordinated swarm to conduct reconnaissance tasks effectively.
\end{itemize}
